---
title: "Lab 5"
author: "Lukas Robinson"
date: "2/23/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
iris<-as_tibble(iris)
```

1.Rename each variable so that it is all lower-case and uses an underscore _ instead of a period . in the name (the recommended coding style in the tidyverse style guide). Print the resulting table.

```{r}
flower_sample_size<-rename(
  iris,
  sepal_length=Sepal.Length,
  sepal_width=Sepal.Width,
  petal_length=Petal.Length,
  petal_width=Petal.Width,
  species=Species
)
flower_sample_size
```

2.Convert the four numerical variables from cm to mm by multiplying by 10. Print the resulting table.

```{r}
mm<-mutate(
  flower_sample_size,
  petal_length = petal_length * 10,
  petal_width = petal_width * 10,
  sepal_length=sepal_length*10,
  sepal_width=sepal_width*10
)
mm
```

3.Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.

```{r}
area<-mutate(mm,sepal_area = sepal_length*sepal_width,
             petal_area=petal_length*petal_width)
species_area<-select(area,sepal_area,petal_area,species
)
species_area
```

4.Calculate the following statistics for the entire dataset from the sepal length variable and print the resulting table:

sample size
maximum value
minimum value
range
median
first quartile (q1)
third quartile (q2)
inter-quartile range (iqr)

```{r}
sepal_summary<-summarize(mm, sample_size = n(),
          max=max(sepal_length),
          min=min(sepal_length),
          range=max-min,
          med=median(sepal_length),
          q1=quantile(sepal_length, .25),
          q3=quantile(sepal_length, .75),
          IQR=IQR(sepal_length)
)
sepal_summary
```

5.Calculate the following statistics for each species from the petal width variable and print the resulting table:

sample size
mean
standard deviation
variance
standard error of the mean
approximate 95% confidence interval

```{r}
petals_grouped<-group_by(mm, species)
petals_grouped

summarize(petals_grouped,mean_width=mean(petal_width))

petal_summary<-summarize(
           petals_grouped,
           sampl_size=n(),
           mean=mean(petal_width),
           sd=sd(petal_width),
           var=var(petal_width),
           sem=sd/sqrt(sampl_size),
           ci_upper=mean+2*sem,
           ci_lower=mean-2*sem
)
petal_summary
```

6.Visualize the relationship between petal width and species using a strip plot.

```{r}
mm_striplot<-ggplot(data=mm)+
  geom_jitter(mapping=aes(x=species,y=petal_length), alpha =.4
)
mm_striplot
```

7.Starting with the previous graph, add the mean and 95% confidence interval for each species.

```{r}
ggplot(data=mm)+
  geom_jitter(mapping=aes(x=species,y=petal_width), alpha =.4)+
  geom_crossbar(
    data=petal_summary,
    mapping=aes(x=species, y=mean,ymax=ci_upper,
                ymin=ci_lower),
    color="red"
  )
```

8.Visualize the relationship between petal length, petal width, and species using a scatterplot. Map the two numerical variables to the x and y axes and map species to the color and shape aesthetics.

```{r}
ggplot(data=mm)+
  geom_point(mapping=aes(x=petal_width,y=petal_length,color=species))
```

```{r}
sessioninfo::session_info()
```

